Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-08-02 manuscript/climate_sensitivity_draft.Rmd
Update climate_sensitivity_draft.Rmd
move comparison of droughts to be the last question/hypothesis, merge drought strength and response questions.

*First, how significant is the effect of individual drought years?*
Droughts are rarely explicitly defined in ecological studies [@slette_how_2019], yet no two droughts are the same. This study addressed this by analyzing trees' resistance to drought within and across three defined drought periods.

*Second, what drives the observed tendency for large trees to suffer more during drought?*  
[@bennett_larger_2015] showed that in forests globally, large trees suffer greater growth reductions during drought. However, this analysis quantified tree size based on DBH, which has no direct mechanistic meaning. This study proposed three major mechanisms (besides insects): (1) inherently greater biophysical challenge of being tall; (2) greater exposure of the crowns of large trees; and (3) greater water availability. It is also expected that roots play a role, though these hypotheses still need to be tested.

*Third, how do species' traits influence drought response?* 
Analyzing drought responses on the species level does not fully explain mechanisms and is not feasible in diverse forests. The solution is a trait-based approach. Leaf hydraulic traits hold more promise than more commonly/traditionally-measured traits such as wood density and SLA (Medeiros et al.).

*Fourth, how do tree size and functional traits interact to influence drought response?*
It is possible that the pattern observed by [@bennett_larger_2015] could be caused by smaller trees being more drought resistant. Alternatively, larger trees may have more drought-resistant traits as adpatations to greater biophysical challenges.

@@

**2. Why do larger trees suffer greater growth declines during drought?**
Our forest displays the same trend as most forests globally [@bennett_larger_2015]. (Note that Bennett et al. 2015 identified only one study on tree growth responses to drought in the Eastern US temperate deciduous biome. We know little about how tree size shapes drought response in this biome.)

@@

**I think for #4 here the focus should be on hypotheses looking at the overall trend compared to the specific scenarios?**

>>>>

*First, what drives the observed tendency for large trees to suffer more during drought?*  
[@bennett_larger_2015] showed that in forests globally, large trees suffer greater growth reductions during drought. However, this analysis quantified tree size based on DBH, which has no direct mechanistic meaning. This study proposed three major mechanisms (besides insects): (1) inherently greater biophysical challenge of being tall; (2) greater exposure of the crowns of large trees; and (3) greater water availability. It is also expected that roots play a role, though these hypotheses still need to be tested.

*Second, how do species' traits influence drought response?* 
Analyzing drought responses on the species level does not fully explain mechanisms and is not feasible in diverse forests. The solution is a trait-based approach. Leaf hydraulic traits hold more promise than more commonly/traditionally-measured traits such as wood density and SLA (Medeiros et al.).

*Third, how do tree size and functional traits interact to influence drought response?*
It is possible that the pattern observed by [@bennett_larger_2015] could be caused by smaller trees being more drought resistant. Alternatively, larger trees may have more drought-resistant traits as adpatations to greater biophysical challenges.

*Fourth, how significant is the effect of individual drought years?*
Droughts are rarely explicitly defined in ecological studies [@slette_how_2019], yet no two droughts are the same. This study addressed this by analyzing trees' resistance to drought within and across three defined drought periods.

@@

**1. Why do larger trees suffer greater growth declines during drought?**
Our forest displays the same trend as most forests globally [@bennett_larger_2015]. (Note that Bennett et al. 2015 identified only one study on tree growth responses to drought in the Eastern US temperate deciduous biome. We know little about how tree size shapes drought response in this biome.)

@@

[differences among droughts:]
**I think for #4 here the focus should be on hypotheses looking at the overall trend compared to the specific scenarios?**
